Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-06-15 Scripts/Initial_Analysis.Rmd
Produced first set of potential figures

# Load all sp in noe table
Eme_Res <- bind_rows(lapply(Paths, fread))
# warnings() for empty data species

@@

# Per Stock
stock_d_hist <- Eme_Res %>% 
  filter(
    n_ens == 10,
    emerging_yr >= 2020
  ) %>% 
  group_by(emerging_yr,taxon_key) %>%
  # summarise(n_tax = length(unique(eez_name))) %>%
  summarise(n()) %>% 
  mutate(
    level = "stock"
  ) %>% 
  select(1,3,4)
  # ggplot() +
  # geom_histogram(
  #   aes(
  #     x = emerging_yr
  #   ),
  #   stat = "count"
  # )

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  filter(
    n_ens == 10,
    emerging_yr >= 2020
  ) %>% 
  group_by(emerging_yr,eez_name) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(n()) %>% 
  mutate(
    level = "EEZ"
  ) %>% 
  select(1,3,4)

@@

@@

Years <-seq(,2100,1)

@@

          F_BData <- Data[1]
          colnames(F_BData) <- 2020

@@

sst_data <- my_path("D",T,"Climate","SST_data.csv",read = T)

ggplot(F_BData) +
  geom_line(
    aes(
      x = as.numeric(year),
      y = mean_temp
    )
  )

@@

>>>>

# Load all sp in noe table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  )
# warnings() for empty data species

@@

# Per Stock
stock_d_hist <- Eme_Res %>% 
  group_by(emerging_yr,taxon_key) %>%
  # summarise(n_tax = length(unique(eez_name))) %>%
  summarise(n()) %>% 
  mutate(
    level = "stock"
  ) %>% 
  select(1,3,4)
  # ggplot() +
  # geom_histogram(
  #   aes(
  #     x = emerging_yr
  #   ),
  #   stat = "count"
  # )

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  group_by(emerging_yr,eez_name) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(n()) %>% 
  mutate(
    level = "EEZ"
  ) %>% 
  select(1,3,4)

@@

##### Time Lapse plot

```{r Time_lapse_plot,  eval = T, echo = T}

# Per Stock
stock_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
    distinct(taxon_key,neighbour_id, .keep_all = TRUE) %>% 
    group_by(taxon_key) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "Stock"
  ) %>% 
    select(1,3,4)

  #  EEZ data
eez_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
  filter(n_ens == 10) %>% 
    distinct(eez_name,neighbour_id, .keep_all = TRUE) %>% 
    group_by(eez_name) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "EEZ"
  ) %>% 
    select(1,3,4)

# Plot Data
plot_data <- stock_d %>% 
  bind_rows(eez_d)

  # filter(emerging_yr >= 2020) %>% 
  ggplot() +
    geom_area(data = subset(plot_data, level == "Stock"),
              aes(
                x = as.numeric(taxon_emer),
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    )  +
    geom_area(data = subset(plot_data, level == "EEZ"),
              aes(
                x = taxon_emer,
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    ) +
    # Comment out for option A (Change plot name!!)
    geom_hline(yintercept = length(unique(Eme_Res$eez_name)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of EEZs", x = 2010, y = length(unique(Eme_Res$eez_name))+10), color = "grey70",size =3) +
    geom_hline(yintercept = length(unique(Eme_Res$taxon_key)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of Taxa", x = 2010, y = length(unique(Eme_Res$taxon_key))+10), color = "grey70",size =3) +
    scale_y_continuous("Cumulatuve Curve",
                       breaks = seq(0,500,50),
                       limits = c(0,500)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2000,2100,10)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
  ggsave("./Figures/figure_accumulative_curve_B.png",
         width = 6,
         height = 6,
         units = "in"
  )
```

@@

Years <-seq(1951,2100,1)

@@

          F_BData <- Data[1]
          colnames(F_BData) <- Years[1]

@@

### NEED TO RUN TIME LAPSE CHUNK FIRST TO GET ACCUMULATIVE DATA

# Get sst_data
sst_data <- my_path("D",T,"Climate","SST_data.csv",read = T)

sst_hist <- sst_data %>% 
  filter(year < 2000) %>% 
  group_by() %>% 
  summarise(hist_sst =mean(mean_temp)) %>% 
  pull()

sst_change <- sst_data %>%
  filter(year > 2020) %>% 
  mutate(chng = round(mean_temp-sst_hist,2))

  # Plot Data
stock_d %>% 
  bind_rows(eez_d) %>% 
  filter(taxon_emer >= 2020) %>% 
  rename(year = taxon_emer) %>% 
  left_join(sst_change) %>% 
  ggplot() +
  geom_line(
    aes(
      x = chng,
      y = com_sum,
      colour = level
    )
  ) +
  geom_hline(yintercept = length(unique(Eme_Res$eez_name)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of EEZs", x = 0.5, y = length(unique(Eme_Res$eez_name))+10), color = "grey70",size =3) +
    scale_y_continuous("Cumulatuve Curve",
                       breaks = seq(0,450,50),
                       limits = c(0,500)
    ) +
    scale_x_continuous("Change in SST (C)",
                       breaks = seq(0,2,0.2),
                       limits = c(0.3,2.3)
    ) +
    my_ggtheme_p() +
    scale_colour_viridis(discrete = T) +
  ggsave("./Figures/figure_temp.png",
         width = 6,
         height = 6,
         units = "in"
  )

@@

data %>% 
  left_join(data_eez,
            by = "emerging_yr") %>% 
  rename(year = emerging_yr) %>% 
  left_join(sst_data) %>% 
  ggplot() +
  geom_point(
    aes(
      x = mean_temp,
      y = emerging_eez,
      fill = year,
      colour = year
    )
  )
